---
title: "Supplemental_figures"
author: "Stephanie Hickey"
date: "7/2/2022"
output: 
  html_document:
    code_folding: hide
---

## Set up
```{r, setup, include=FALSE, message=FALSE}
knitr::opts_knit$set(root.dir = '..')
```

### Load packages etc.
```{r, include=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(patchwork)
library(parallel)
library(ggpubr)
library(rstatix)
source("./src/chronic_inflammation_functions.R")
figure_path = "./results/prediction_clusters_same_graph/figures"
if(!dir.exists(figure_path)){dir.create(figure_path)}
```

### Labeling trait types for the rest of the Figures & Tables
```{r, message=FALSE}
# get complex vs ai labels
c_v_ai = read.csv("./data/diseases_used_in_study.csv", row.names = 1)

#Autoimmune diseases
ai = 
  c_v_ai %>%
  filter(TraitType == "Autoimmune Disease") %>%
  pull(Disease)

#Complex diseases
complex = 
  c_v_ai %>%
  filter(TraitType == "Complex Disease") %>%
  pull(Disease)
```

## Supplemental Table S1: Disease and trait Geneplexus average log2(auPRC/prior) from 3-fold cross validation

Results from `summarizeGeneplexusPredictions.R`
```{r, message=FALSE}
load("./results/GenePlexus_parameter_checks/Geneplexus_summary_new_networks.Rdata")

# we did not use these in the analysis
remove_traits = c("Colitis","Height_gene_shot")

S1 = 
  summary_df %>%
  dplyr::rename(PredictionNetwork = Network) %>%
  filter(!Disease %in% c(remove_traits, "chronic_inflammation_go"))

# save
write.csv(S1, 
          file = paste0(figure_path, "/TableS1_CV_Scores.csv"), 
          row.names = F)
```

## Supplemental Table S2: Disease and trait genes
```{r,  message=FALSE}
# load the disease genes from disgenet or pascal
files = list.files("./data/disease_gene_files", 
                   pattern = ".txt",
                   full.names = TRUE)

temp = lapply(files, read.delim)

dgdf = do.call(rbind, temp) 

dgdf = 
  dgdf %>%
  dplyr::rename(EntrezID = Gene) %>%
  filter(!Disease %in% remove_traits) %>%
  mutate(TraitType =
           case_when(Disease %in% ai ~ "Autoimmune Disease",
                     Disease %in% complex ~ "Complex Disease",
                     !Disease %in% c(ai, complex)  ~ "Non-disease Trait"))

# add gene symbol
symbols = entrez2symbol(as.character(dgdf$EntrezID))
dgdf$GeneSymbol = symbols

# rearrange cols
S2 = 
  dgdf %>%
  select(GeneSymbol, 
         EntrezID, 
         Disease, 
         TraitType)
# save
write.csv(S2, 
          file = paste0(figure_path, "/TableS2_seed_genes.csv"), 
          row.names = F)
```

## Supplemental Table S3: Gene/Cluster assignments
### Load gene to cluster assignment files
```{r, message=FALSE}
loadClusters = function(cluster_path){
  
  files = list.files(cluster_path, full.names = T, pattern = ".csv")
  # remove fake trait clusters
  files = files[grep("Fake_", files, invert=TRUE)]
  # load
  clust_list = mclapply(files, 
                      read.csv, 
                      row.names = 1,
                      mc.cores = detectCores()-1)
  # bind list
  clust_df = do.call(rbind, clust_list)
  return(clust_df)
}

cluster_dir = "./data_Zenodo/prediction_clusters_same_graph/clusters/"

string = loadClusters(paste0(cluster_dir, "predicted_withSTRING--clustered_on_STRING"))
string_exp = loadClusters(paste0(cluster_dir, "predicted_withSTRING-EXP--clustered_on_STRING-EXP"))
string_string_exp = loadClusters(paste0(cluster_dir, "predicted_withSTRING--clustered_on_STRING-EXP"))
biogrid = loadClusters(paste0(cluster_dir, "predicted_withBioGRID--clustered_on_BioGRID"))
cpdb = loadClusters(paste0(cluster_dir, "predicted_withConsensusPathDB--clustered_on_ConsensusPathDB"))

# bind dfs together
clust_list = list(string, string_exp, string_string_exp, biogrid, cpdb)
clust_df = do.call(rbind, clust_list)

# mark inflammatory gene sets if any
inflamm = unique(clust_df$Disease[grep("inflamm", clust_df$Disease)])

# add trait type to the cluster df
clust_df = 
  clust_df %>%
  mutate(TraitType =
           case_when(Disease %in% ai ~ "Autoimmune Disease",
                     Disease %in% complex ~ "Complex Disease",
                     Disease %in% inflamm ~ "Inflammation Gene Set",
                     !Disease %in% c(ai, complex, inflamm)  ~ "Non-disease Trait"))

remove_traits = c(inflamm,
                  "Colitis",
                  "Height_gene_shot")
clust_df = 
  clust_df %>%
  filter(!Disease %in% remove_traits)
```

### Add GenePlexus prediction average 3-fold CV for each disease/prediction network combo
Also has number of seed genes. Filter for >= 15
```{r, message=FALSE}
summary_df = 
  summary_df %>%
  dplyr::rename(PredictionNetwork = Network) %>%
  filter(!Disease %in% remove_traits) %>%
  select(Disease,  
         PredictionNetwork, 
         CVscore,
         nSeeds,
         TraitType) 

clust_df = 
  clust_df %>%
  left_join(summary_df) 
```

### Remove diseases/traits where no permuted traits clustered. 
Without permuted traits with clusters with at least five genes we can't compute overlap p-values.
```{bash, eval = F}
# out files from submit_clusterRandomGenes.R
cd ./run/sbatches_clusterRandomGenes
grep -hnr --with-filename "number clustered" *STRING-EXP.out > STRING-EXP_number_clustered.txt
grep -hnr --with-filename "number clustered" *STRING.out > STRING_number_clustered.txt
grep -hnr --with-filename "number clustered" *BioGrid.out > BioGrid_number_clustered.txt
grep -hnr --with-filename "number clustered" *ConsensusPathDB.out > ConsensusPathDB_number_clustered.txt
```
```{r,message=FALSE, include=TRUE}
files = list.files("./data",
                   pattern = "_number_clustered.txt",
                   full.names = T)

graph_name = gsub("_number_clustered.txt", "", basename(files))

nclust_list = lapply(files, read.delim, header = F, sep = " ")

for(i in 1:length(nclust_list)){
  
  nclust_list[[i]]$nFakesClustered = gsub("number clustered = ", "", nclust_list[[i]]$V2)
  nclust_list[[i]]$nFakesClustered = as.numeric(nclust_list[[i]]$nFakesClustered)
  nclust_list[[i]]$Disease = gsub(paste0("_",graph_name[i],".*"), "", nclust_list[[i]]$V1)
  nclust_list[[i]]$ClusterGraph = graph_name[i]
}

nclust = 
  do.call(rbind, nclust_list) %>%
  select(ClusterGraph, 
         nFakesClustered, 
         Disease)

nclust = 
  nclust %>%
  filter(!Disease %in% remove_traits) %>%
  mutate(TraitType =
           case_when(Disease %in% ai ~ "Autoimmune Disease",
                     Disease %in% complex ~ "Complex Disease",
                     Disease %in% inflamm ~ "Inflammation Gene Set",
                     !Disease %in% c(ai, complex, inflamm)  ~ "Non-disease Trait"))

nclust$ClusterGraph = gsub("BioGrid", "BioGRID", nclust$ClusterGraph)

# join with nclust
clust_df = 
  clust_df %>%
  left_join(nclust)
```

### Merge with GenePlexus prediction scores
```{r, message=FALSE}
pred_path = "./data_Zenodo/GenePlexus_output"
gp_files = list.files(pred_path, full.names = TRUE)
gp_files = gp_files[grep("--DisGeNet--predictions.tsv", gp_files)]
gp_files = gp_files[grep("inflamm", gp_files, invert = TRUE)]

gp_list = mclapply(gp_files, 
                   read.delim,
                   mc.cores= detectCores()-1)

file_name_split = str_split(basename(gp_files), pattern = "--")
dis_names = unlist(lapply(file_name_split, function(x) x[[1]]))
prednet = unlist(lapply(file_name_split, function(x) x[[2]]))

for(i in 1:length(gp_list)){
  
  gp_list[[i]]$Disease = dis_names[i]
  gp_list[[i]]$PredictionNetwork = prednet[i]
  
}

gpdf = do.call(rbind, gp_list)
```

### Filter, arrange, and save
```{r, message=FALSE}
S3 = 
  clust_df %>%
  filter(nSeeds >= 15,
         CVscore >= 1,
         nFakesClustered > 0,
         !Disease %in% remove_traits) %>%
  dplyr::rename(nClusteredPermutations = nFakesClustered,
                Entrez = Gene) %>%
  left_join(gpdf) %>%
  dplyr::select(PredictionNetwork,
                ClusterGraph,
                Disease,
                TraitType,
                nClusteredPermutations,
                Cluster,
                Entrez,
                Symbol,
                Probability,
                GeneType)

write.csv(S3, 
          file = paste0(figure_path, "/TableS3_gene_cluster_assignments.csv"), 
          row.names = F)
```

## Supplemental Table S4: Chronic inflammation gene sets with GenePlexus predictions
```{r, message=FALSE}
pred_path = "./data_Zenodo/GenePlexus_output"
ci_files = list.files(pred_path, pattern = "inflamm", full.names = TRUE)
ci_files = ci_files[grep("--GO--predictions.tsv", ci_files)]

ci_list = mclapply(ci_files, 
                   read.delim,
                   mc.cores= detectCores()-1)

file_name_split = str_split(basename(ci_files), pattern = "--")
ci_names = unlist(lapply(file_name_split, function(x) x[[1]]))
prednet = unlist(lapply(file_name_split, function(x) x[[2]]))

for(i in 1:length(ci_list)){
  
  ci_list[[i]]$ChronicInflammationSource = ci_names[i]
  ci_list[[i]]$PredictionNetwork = prednet[i]
  
}

cidf = do.call(rbind, ci_list)

S4 = 
  cidf %>%
  filter(!ChronicInflammationSource %in% 
           c("chronic_inflammation_go",
           "chronic_inflammatory_response_GO2EG")) %>%
  mutate(GeneType = case_when(Class.Label == "P" ~ "seed",
                              Class.Label != "P" & Probability >= .80 ~ "predicted CI-associated",
                              Class.Label != "P" & Probability < .80 ~ "not likely CI-associated")) %>%
  select(-Name, -Class.Label) 

write.csv(S4, 
          file = paste0(figure_path, "/TableS4_CI_genes.csv"), 
          row.names = F)

```

## Supplemental Table S5: CI-overlap results
```{r, message=FALSE}
files = 
  list.files("./data_Zenodo/prediction_clusters_same_graph/scores",
                   pattern = ".Rdata",
                   full.names = T)

res_list = lapply(files, loadRData)

res_list = lapply(res_list, 
                  function(x){
                    x$ChronicInfThreshold = as.character(x$ChronicInfThreshold);
                    x
                  })

res_df = do.call(rbind, res_list)

# add TraitType to res_df
res_df = 
  res_df %>%
  filter(!Disease %in% remove_traits) %>%
  mutate(TraitType =
           case_when(Disease %in% ai ~ "Autoimmune Disease",
                     Disease %in% complex ~ "Complex Disease",
                     !Disease %in% c(ai, complex)  ~ "Non-disease Trait"))

# add cv score 
S5 = 
  res_df %>%
  left_join(summary_df) %>%
  filter(CVscore >= 1,
         nSeeds >= 15)

colnames(S5) = c(
  "ChronicInflammationSource",
  "nChronicInflammationSourceGenes",
  "Cluster",
  "nClusterGenes",
  "nOverlap",
  "phyperPval",
  "Enrichment",
  "Disease",
  "ChronicInf",
  "ChronicInfThreshold",
  "ClusterGraph",
  "PredictionNetwork",
  "phyperFDR",
  "TraitType",
  "PermutedPval",
  "PermutedFDR",
  "nClustersFromPermutedSets",
  "CVscore",
  "nSeeds")

S5 = 
  S5 %>%
  ungroup() %>%
  select(PredictionNetwork,
         ClusterGraph,
         ChronicInflammationSource,
         Disease,
         Cluster,
         nOverlap,
         nChronicInflammationSourceGenes,
         nClusterGenes,
         Enrichment,
         PermutedPval,
         PermutedFDR,
         nClustersFromPermutedSets)

write.csv(S5, 
          file = paste0(figure_path, "/TableS5_CI_overlap_results.csv"), 
          row.names = F)
```

## Supplemental Table S6: Number of diseases considered for CI overlap
We included a disease if it:  

  - had cv > 1 on the prediction network
  - had clusters with at least 5 genes
  - had at least 1 permuted gene list that has clusters with at least 5 genes
  
```{r, message=FALSE, include=TRUE}
# total diseases
disease_tally = 
  summary_df %>%
  filter(nSeeds >= 15,
         TraitType != "Inflammation Gene Sets") %>%
  group_by(TraitType, PredictionNetwork) %>%
  tally(name = "nTotal")

# Traits in each category with CV score > 1
cv_tally = 
  summary_df %>%
  filter(CVscore >= 1) %>%
  group_by(TraitType, PredictionNetwork) %>%
  tally(name = "nCV1") %>%
  arrange(PredictionNetwork)

disease_tally = 
  left_join(disease_tally, cv_tally) %>%
  select(TraitType,
         PredictionNetwork,
         nTotal,
         nCV1)

# Traits that clustered
nClustered = 
  clust_df %>%
  select(Disease, 
         PredictionNetwork,
         ClusterGraph,
         TraitType) %>%
  distinct() %>%
  group_by(PredictionNetwork,
           ClusterGraph,
           TraitType) %>%
  tally(name= "nClustered")

# Traits that clustered with CV >=1
nClusteredCV1 = 
  clust_df %>%
  filter(CVscore >=1) %>%
  select(Disease, 
         PredictionNetwork,
         ClusterGraph,
         TraitType) %>%
  distinct() %>%
  group_by(PredictionNetwork,
           ClusterGraph,
           TraitType) %>%
  tally(name= "nClusteredCV1")

# n traits where at least one fake trait clustered
fakes_clustered_tally = 
  nclust %>%
  filter(nFakesClustered > 0) %>%
  group_by(TraitType, ClusterGraph) %>%
  tally(name = "nFakesClustered") %>%
  arrange(ClusterGraph)

#Traits that clustered with CV >=1 and > 0 Fakes clustered
clust_df = 
  clust_df %>%
  left_join(nclust)

nClusteredCV1Fakes = 
  clust_df %>%
  filter(CVscore >=1,
         nFakesClustered > 0,
         ClusterGraph == "ConsensusPathDB",
         TraitType == "Non-disease Trait") %>%
  pull(Disease) %>% unique()
         
nClusteredCV1Fakes = 
  clust_df %>%
  filter(CVscore >=1,
         nFakesClustered > 0) %>%
  select(Disease, 
         PredictionNetwork,
         ClusterGraph,
         TraitType) %>%
  distinct() %>%
  group_by(PredictionNetwork,
           ClusterGraph,
           TraitType) %>%
  tally(name= "nClusteredCV1withFakes")

disease_tally = 
  left_join(disease_tally, nClustered) %>%
  left_join(fakes_clustered_tally) %>%
  left_join(nClusteredCV1) %>%
  left_join(nClusteredCV1Fakes)

# Traits with clusters with at least 5 genes
nGenesPerCluster = 
  clust_df %>%
  group_by(Disease,
           Cluster,
           PredictionNetwork,
           ClusterGraph,
           TraitType) %>%
  tally()

nClustered5 = 
  nGenesPerCluster %>%
  filter(n >= 5) %>%
  ungroup() %>%
  select(-Cluster, -n) %>%
  distinct() %>%
  group_by(TraitType,
           PredictionNetwork,
           ClusterGraph) %>%
  tally(name = "nClustered5")

# Traits with clusters with at least 5 genes and CV >= 1
nGenesPerCluster = 
  clust_df %>%
  filter(CVscore >=1) %>%
  group_by(Disease,
           Cluster,
           PredictionNetwork,
           ClusterGraph,
           TraitType) %>%
  tally()

nClustered5CV1 =
  nGenesPerCluster %>%
  filter(n >= 5) %>%
  ungroup() %>%
  select(-Cluster, -n) %>%
  distinct() %>%
  group_by(TraitType,
           PredictionNetwork,
           ClusterGraph) %>%
  tally(name = "nClustered5CV1")

# Traits with clusters with at least 5 genes and CV >= 1 and >0 clustered permuted traits
nGenesPerCluster = 
  clust_df %>%
  filter(CVscore >=1,
         nFakesClustered > 0) %>%
  group_by(Disease,
           Cluster,
           PredictionNetwork,
           ClusterGraph,
           TraitType) %>%
  tally()

nClustered5CV1fakes =
  nGenesPerCluster %>%
  filter(n >= 5) %>%
  ungroup() %>%
  select(-Cluster, -n) %>%
  distinct() %>%
  group_by(TraitType,
           PredictionNetwork,
           ClusterGraph) %>%
  tally(name = "nClustered5CV1withFakes")

disease_tally = 
  left_join(disease_tally, nClustered5) %>%
  left_join(nClustered5CV1) %>%
  left_join(nClustered5CV1fakes)

###Number of traits with CV >=1 that cluster with 100 iterations of the Leiden algorithm, and/or have at least one cluster containing >= 5 genes.

disease_tally = 
  disease_tally %>%
  dplyr::rename(nPermutedClustersSize5 = nFakesClustered,
                      nClustersSize5 = nClustered5,
                      nFinal = nClustered5CV1withFakes) %>%
               select(-nClustered,
                      -nClusteredCV1,
                      -nClusteredCV1withFakes,
                      -nClustered5CV1)

write.csv(disease_tally, file = paste0(figure_path, "/TableS6.csv"))
S6 = disease_tally 

knitr::kable(disease_tally)
```

## Supplemental Table S7: CI-signature group assignments
Only includes ConsensusPathDB clusters. See Fig3_TabS7_TabS8.Rmd

## Supplemental Table S8: GOBP enrichments for CI-signature groups 
Only includes ConsensusPathDB clusters. See Fig3_TabS7_TabS8.Rmd

## Supplemental Table S9: SAveRUNNER results
Only includes ConsensusPathDB clusters. See Fig4_TabS9.Rmd

## Figure S1: Number of genes in each inflammation geneset
```{r, fig.width=10, fig.height=8, fig.cap = "Fig. S1: Number of seed and Geneplexus predicted by each network in inflammation genes in each gene set"}

P = 
cidf %>%
  filter(Probability >= .80,
         !ChronicInflammationSource %in% c("chronic_inflammation_go", 
                                           "chronic_inflammatory_response_GO2EG")) %>%
  ggplot(aes(x = ChronicInflammationSource, 
             fill = Class.Label)) +
  geom_bar() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, 
                                   hjust=1)) +
  theme(legend.position="bottom") +
  ylab("Number of Genes") + 
  theme(axis.text = element_text(size = 8)) +
  facet_wrap(~PredictionNetwork, ncol = 2) 

ggsave(P, 
       file = paste0(figure_path,
                     "/FigS1_nChronicInflammation_seed_genes.png"),
       width = 7, 
       height = 7, 
       dpi = 300)

P
```

## Figure S2: Proportion of traits overlapping at least one chronic inflammation cluster 
```{r, fig.width=8, fig.height=10, message = FALSE, fig.cap = "Fig S2: Proportion of traits with at least one CI-enriched cluster. The top network is the network used for Geneplexsus prediction, the bottom network was used for clustering"}
       
res_list = 
  res_df %>%
  group_by(Group1,
           PredictionNetwork,
           ClusterGraph) %>%
  group_split()

tallySigDiseases = function(df, cutoff){
  
  sig_disease = 
    df %>%
    filter(PermutedFDR < cutoff,
           Enrichment > 0) %>%
    select(Disease, 
           TraitType,
           PredictionNetwork,
           ClusterGraph,
           ChronicInfThreshold,
           Group1) %>%
    distinct() %>%
    mutate(Signficant_Overlap = "Yes")
  
  not_sig_diseases = 
    df %>%
    filter(!Disease %in% sig_disease$Disease) %>%
    select(Disease, 
           TraitType,
           PredictionNetwork,
           ClusterGraph,
           ChronicInfThreshold,
           Group1) %>%
    distinct() %>%
    mutate(Signficant_Overlap = "No")
  
  # bind 
  sig_disease = rbind(sig_disease, not_sig_diseases)
  
  return(sig_disease)
}

sig_disease_list = lapply(res_list, tallySigDiseases, cutoff = .05)
sig_disease_df = do.call(rbind, sig_disease_list)

tally_sig_disease =
  sig_disease_df %>%
  group_by(TraitType,
           PredictionNetwork,
           ClusterGraph,
           Group1,
           Signficant_Overlap) %>%
  tally() %>%
  pivot_wider(names_from = Signficant_Overlap, 
              values_from = n, 
              values_fill = 0) %>%
  mutate(Total = Yes + No) %>%
  mutate(PropSig = Yes/Total)

# plot 
tally_sig_disease$TraitType = factor(tally_sig_disease$TraitType, 
                                   levels = c("Autoimmune Disease",
                                              "Complex Disease",
                                              "Non-disease Trait"))
Fig2a = 
  tally_sig_disease %>%
  filter(!Group1 %in% c("chronic_inflammation_go", 
                        "chronic_inflammatory_response_GO2EG")) %>%
  ggplot(aes(x = TraitType,
             y = PropSig,
             fill = Group1)) +
  geom_col() +
  theme_classic() +
  xlab("Trait type") +
  ylab("Proportion diseases with CI Overlap") +
  guides(fill = guide_legend("CI gene set")) +
  coord_flip() +
  theme(legend.position="none",
        text = element_text(size = 8),
        strip.text = element_text(size = 5.5),
        ) + 
  facet_wrap(~PredictionNetwork + ClusterGraph + Group1,
             ncol = 3)

ggsave(Fig2a, 
       file = paste0(figure_path,
                     "/FigS2_proportion_clustered_FDR05.png"),
       width = 7, 
       height = 10, 
       dpi = 300)

Fig2a
```

## Figure S3-S7: Chronic inflammation association score of non-seed genes in overlapping and non-overlapping clusters. 
```{r, fig.width=7, fig.height=4, message = FALSE, fig.cap = "The top network is the network used for Geneplexsus prediction, the bottom network was used for clustering"}
# merge overlap FDR with cluster assignments

res_clust = 
  res_df %>%
  ungroup() %>%
  dplyr::rename(ChronicInflammationSource = Group1,
         Cluster = Group2) %>%
  left_join(clust_df) %>%
  select(Gene,
         Disease,
         Cluster,
         TraitType,
         PredictionNetwork,
         ClusterGraph,
         ChronicInflammationSource,
         ChronicInfThreshold,
         Enrichment,
         PermutedFDR) %>%
  mutate(SignificantOverlap =
           case_when(PermutedFDR > .05 | Enrichment < 0 ~ FALSE,
                     PermutedFDR <= .05 & Enrichment > 0 ~ TRUE)) %>%
  filter(!is.na(PermutedFDR)) # clusters with fewer than 5 genes
  
# merge with chronic inflammation GenePlexus predictions

cidf = 
  cidf %>% # all predictions bound into one file
  select(Entrez,
         Probability,
         Class.Label,
         PredictionNetwork,
         ChronicInflammationSource) %>%
  dplyr::rename(Gene = Entrez)
  
clust_pred = 
  left_join(res_clust, cidf) %>%
  mutate(CI_GeneType = 
           case_when(ChronicInfThreshold == "P" & Class.Label == "P"  ~ "Seed",
                     ChronicInfThreshold == "P" & Class.Label != "P" ~ "not Seed",
                     ChronicInfThreshold == 0.8 & Probability >= 0.8 ~ "Seed",
                     ChronicInfThreshold == 0.8 & Probability < 0.8 ~ "not Seed")) 

# merge with CVscores
clust_pred = 
  left_join(clust_pred, summary_df)
  
clust_pred_mean = 
  clust_pred %>%
  group_by(Cluster,
           ClusterGraph,
           PredictionNetwork,
           ChronicInflammationSource,
           ChronicInfThreshold,
           CI_GeneType) %>%
  mutate(MeanProb = mean(Probability)) %>%
  select(Cluster, 
         TraitType,
         ClusterGraph, 
         PredictionNetwork,
         ChronicInflammationSource,
         ChronicInfThreshold,
         CI_GeneType,
         MeanProb,
         SignificantOverlap,
         CVscore) %>%
  distinct()

# pvals
clust_pred_mean_filt = 
  clust_pred_mean %>%
  filter(CI_GeneType == "not Seed",
         TraitType != "Non-disease Trait", # plot only real diseases
         !ChronicInflammationSource %in% c("chronic_inflammation_go",                 
                                           "chronic_inflammatory_response_GO2EG"))

clust_pred_mean_filt$SignificantOverlap = factor(clust_pred_mean_filt$SignificantOverlap, 
                                            levels = c("FALSE",
                                                       "TRUE"))
pred_mean_wilcox = 
  clust_pred_mean_filt %>%
  group_by(ClusterGraph, 
           PredictionNetwork, 
           ChronicInflammationSource) %>%
  wilcox_test(formula = MeanProb ~ SignificantOverlap,  p.adjust.method = "BH") %>%
  adjust_pvalue(method = "BH") %>%
  add_significance("p.adj") %>%
  add_y_position(formula = MeanProb ~ SignificantOverlap, 
                   fun = "max")

# plot
n = 2
for(pn in unique(clust_pred_mean_filt$PredictionNetwork)){
if(pn == "STRING"){next}
n = n + 1
plot_p = 
  pred_mean_wilcox %>%
  filter(PredictionNetwork == pn) 

p1 = 
  clust_pred_mean_filt %>%
  filter(PredictionNetwork == pn) %>% 
  ggplot(aes(x = SignificantOverlap, 
             y = MeanProb,
             fill = ChronicInflammationSource)) +
  geom_boxplot() +
  ylab("mean probability per cluster") +
  theme_classic() +
   theme(legend.position="none",
        text = element_text(size = 8),
        strip.text = element_text(size = 5.5),
        strip.text.x = element_text(margin = margin(.1, 0, .1, 0, "cm"))
        ) + 
  facet_wrap(~PredictionNetwork + ClusterGraph + ChronicInflammationSource,
             ncol = 3, scales = "free_y") +
  stat_pvalue_manual(plot_p, label = "p.adj.signif", tip.length = 0.01) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))

ggsave(p1, 
       file = paste0(figure_path,
                     "/FigS", n, "_mean_pred_non_seed_", pn, ".png"),
       width = 7, 
       height = 4, 
       dpi = 300)

plot(p1 + ggtitle(paste0("FigS", n, " cluster and predict on ", pn)))

}

n = 5
for(cg in c("STRING", "STRING-EXP")){

n = n + 1

plot_p = 
  pred_mean_wilcox %>%
  filter(PredictionNetwork == "STRING",
         ClusterGraph == cg)

p1 = 
  clust_pred_mean_filt %>%
  filter(PredictionNetwork ==  "STRING",
         ClusterGraph == cg) %>% 
  ggplot(aes(x = SignificantOverlap, 
             y = MeanProb,
             fill = ChronicInflammationSource)) +
  geom_boxplot() +
  ylab("mean probability per cluster") +
  theme_classic() +
   theme(legend.position="none",
        text = element_text(size = 8),
        strip.text = element_text(size = 5.5),
        strip.text.x = element_text(margin = margin(.1, 0, .1, 0, "cm"))
        ) + 
  facet_wrap(~PredictionNetwork + ClusterGraph + ChronicInflammationSource,
             ncol = 3, scales = "free_y") +
  stat_pvalue_manual(plot_p, label = "p.adj.signif", tip.length = 0.01) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))

ggsave(p1, 
       file = paste0(figure_path,
                     "/FigS", n, "_mean_pred_non_seed_STRING_",cg,".png"),
       width = 7, 
       height = 4, 
       dpi = 300)

plot(p1 + ggtitle(paste0("FigS", n, "- predict on STRING, cluster on ", cg)))
}
```








